---
title: "Dictionary of Tukita"
format: html
editor: source
css: styles.css
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false
knitr::opts_chunk$set(echo = FALSE)
```

The dictionary was compiled in 2020 by P. Magomedgadzhieva and M. Daniel (Linguistic Convergence Laboratory, HSE University) and updated in 2023. The online version was prepared by G. Moroz (originally by V. Morozova). The compilation of the dictionaries was supported by the University of Jena and by the Basic Research Program at the National Research University "Higher School of Economics" (HSE) as part of the Russian Academic Excellence Project '5-100'. You can always contact us via [email](mailto:misha.daniel@gmail.com) or leave an issue on the [GitHub page](https://github.com/LingConLab/TukitaDict/issues/new).

Please refer to the dictionary as follows:

```{r}
library(RefManageR)
BibOptions(check.entries = FALSE, style = 'text', bib.style = 'authoryear')
article_citation <- BibEntry(bibtype = 'misc', 
 key='magomedgadzhieva2023',
 title='Dictionary of Tukita (v2.0.0)',
 author='Patimat Magomedgazhieva and Michael Daniel',
 year='2023',
 publisher='Linguistic Convergence Laboratory, NRU HSE',
 address='Moscow',
 url='http://lingconlab.ru/TukitaDict/')
```

::: {.panel-tabset}

### Plain text
```{r, results = 'asis'}
print(article_citation, .opts = list(style = 'text'))
```

### BibTeX

```{r}
print(article_citation, .opts = list(style = 'Bibtex'))
```

:::

```{r}
#| echo: false
#| warning: false

library(tidyverse)
library(DT)
library(glue)

read_csv("data/data.csv", show_col_types = FALSE) %>%
  mutate_all(function(i){ifelse(is.na(i), "", i)}) %>% 
  mutate(tooltip = str_c(prs, form2, form3, sep = "; "),
         tooltip = str_remove(tooltip, "^; "),
         tooltip = str_remove(tooltip, ";$"),
         more = '&oplus;',
         tooltip_id = str_c(str_c("kk:&nbsp;", kk), 
                            str_c("jena200:&nbsp;", jena200), 
                            str_c("gld110:&nbsp;", gld110), sep = " "),
         id = glue('<a href="#" data-tooltip data-tooltip-message="{tooltip_id}">{id}</a>')) %>% 
  select(more, tooltip, additional_forms, def_RU, context, id, Russian, English, orthography, transcription, pos) %>% 
  datatable(filter = 'top', escape = FALSE, rownames = FALSE,
            colnames = c("", "tooltip", "additional_forms", "meaning", "context", "id", "Russian", "English", "orthography", "transcription", "pos"),
            options = list(pageLength = 10, dom = 'top', 
                           columnDefs = list(
                             list(visible = FALSE, targets = c(1, 2, 3, 4, 5)),
                             list(orderable = FALSE, className = 'details-control', targets = 0))),
            callback = JS(readLines("plus.js")))
```


